---
title: "quiz getting data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(readxl)
library(lubridate)
library(tidyverse)


```

# Load Files

```{r}
#train sets
x_train <- read.table("./Data/UCI HAR Dataset/train/X_train.txt")
y_train <- read.table("./Data/UCI HAR Dataset/train/y_train.txt")
subject_train <- read.table("./Data/UCI HAR Dataset/train/subject_train.txt")

#test sets
x_test <- read.table("./Data/UCI HAR Dataset/test/X_test.txt")
y_test <- read.table("./Data/UCI HAR Dataset/test/y_test.txt")
subject_test <- read.table("./Data/UCI HAR Dataset/test/subject_test.txt")

# feature set
features <- read.table('./Data/UCI HAR Dataset/features.txt')

# activity labels set
activityLabels = read.table('./Data/UCI HAR Dataset/activity_labels.txt')

```


# 1. Merges the training and the test sets to create one data set.

```{r}
colnames(x_train) <- features[,2]
colnames(y_train) <-"activityId"
colnames(subject_train) <- "subjectId"

colnames(x_test) <- features[,2] 
colnames(y_test) <- "activityId"
colnames(subject_test) <- "subjectId"

colnames(activityLabels) <- c('activityId','activityType')

train_final <- cbind(y_train, subject_train, x_train)
test_final <- cbind(y_test, subject_test, x_test)
base_consolidada <- rbind(train_final, test_final) #Merged Data
vector_names <- names(base_consolidada)
```

# Extracts only the measurements on the mean and standard deviation for each measurement.

```{r}

activity_columns <- str_detect(vector_names, "activity")
subject_columns <- str_detect(vector_names, "subject")
mean_columns <- str_detect(vector_names, "mean")
std_columns <- str_detect(vector_names, "std")

base_filtrada <- base_consolidada[,activity_columns|subject_columns|mean_columns|std_columns] #Filtered Data

```

# Uses descriptive activity names to name the activities in the data set
# Appropriately labels the data set with descriptive variable names.

```{r}

base_final <- left_join(base_filtrada, activityLabels, by = "activityId") %>% 
  select(activityType, everything())


```

#From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r}

tidy_mean <- aggregate(. ~subjectId + activityId, base_final, mean)



write.table(tidy_mean, "Tidy.txt", row.name=FALSE)


```



